A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-08 pilot-publication/manuscript.Rmd
Start adding outcome results to manuscript

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
```

After training, a total of `r m30d.atls` patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.

>>>>

```{r, echo = FALSE}
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
m30d.ptc <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "PTC"
)
m30d.standard.care <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "Standard care"
)
standard.care.vs.atls.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]
arr.standard.care.atls <- inline_outcome_text(
  standard.care.vs.atls.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)
standard.care.vs.ptc.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]
arr.standard.care.ptc <- inline_outcome_text(
  standard.care.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)
atls.vs.ptc.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]
arr.atls.ptc <- inline_outcome_text(
  atls.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)
```

After training, a total of `r n.m30d.control` (`r p.m30d.control`%) patients in the standard care arm had the primary outcome, compared to `r m30d.atls` patients in the ATLS arm and `r m30d.ptc` patients in the PTC arm. The absolute risk difference between the standard care and ATLS arms (95% CI) was `r arr.standard.care.atls`% units, between the standard care and PTC arms (95% CI) `r arr.standard.care.ptc`% units, and between the ATLS and PTC arms (95% CI) `r arr.atls.ptc`% units.

The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.
